What Makes a Deep Convolutional Representation Good for Visual Recognition?

### 2015-06-05 nips2015.tex
Some tweaks

% \cite{fukushima1980neocognitron, lecun1998gradient, riesenhuber1999hierarchical, krizhevsky2012imagenet}
\newcommand{\expperf}{10-fold cross validation accuracies using the LFW view 2 splits (\cite{LFWTech}, totally 6,000 face pairs) are reported.
Although it is highly desirable to characterize representations from the state-of-the-art face pair matching networks \cite{taigman2014deepface, sun2014deep, schroff2015facenet}, neither those trained networks nor their datasets are publicly available.
Nonetheless, under the hard protocol adopted here (\ie image-restricted, no outside data, data augmentation, or multiple-crop evaluation), the (well-performing) random networks remain competitive against trained networks and do provide good representations in terms of accuracies attained.
} 
%State-of-the-art networks trained on massive private datasets \cite{taigman2014deepface, sun2014deep, schroff2015facenet} do have significantly higher accuracies. %absolute
%However, under the hard protocol adopted here (\ie image-restricted, no outside data), this model remains competitive among neural network-based algorithms.
%accuracy of identifying pairs of different pictures from the same person and rejecting those from different persons

>>>>

% \cite{fukushima1980neocognitron, lecun1998gradient, riesenhuber1999hierarchical, krizhevsky2012imagenet}
\newcommand{\expperf}{10-fold cross validation accuracies using the LFW view 2 splits (\cite{LFWTech}, totally 6,000 face pairs) are reported.
We stress that differential comparison of performance among models, rather than absolute performance was the goal of the present work.
Although it would be desirable to also characterize representations from the state-of-the-art face pair matching networks \cite{taigman2014deepface, sun2014deep, schroff2015facenet}, neither the trained networks nor their datasets are publicly available.
Nonetheless, under the challenging protocol adopted here (\ie image-restricted, no outside data, no data augmentation, or multiple-crop evaluation), the highest-performing among the random networks still can achieve reasonable levels of performance (esp. if more layers are used) and thus we argue they are useful objects of study. 
} 
%State-of-the-art networks trained on massive private datasets \cite{taigman2014deepface, sun2014deep, schroff2015facenet} do have significantly higher accuracies. %absolute
%However, under the hard protocol adopted here (\ie image-restricted, no outside data), this model remains competitive among neural network-based algorithms.
%accuracy of identifying pairs of different pictures from the same person and rejecting those from different persons
